The imprint of global magma oceans on exoplanet demographics

### 2022-09-30 src/tex/ms.tex
describe mass-radius relationship

\subsubsection{Stellar sample from Gaia DR3}
\todo{Which star sample was actually used?}

\subsubsection{Planetary ocurrence rates in orbital period and radius}
\todo[inline]{What is the source of our occurrence rate density from which we draw? We could also use a generative model that directly approximates an observed or theoretical density \citep[e.g.,][]{Schlecker2021b}.}
\begin{note}
    The NASA Exoplanet Program Analysis Group chartered Science Analysis Group 13 (SAG 13)...
    The inferred occurrence rate density can be expressed as a power law in planet radius and period
    \begin{equation}
        \frac{\partial^2n}{\partial \log R \, \partial \log P} = \Gamma R^{\alpha} P^{\beta}
    \end{equation}
that is broken in planet radius, resulting in the free parameters $\Gamma$, $\alpha$, $\beta$, and a breakpoint radius $R_\mathrm{break}$.
\end{note}

\subsubsection{Stellar luminosity tracks}
\todo[inline]{if implemented, describe the luminosity evolution of stars}
\begin{note}
    Planetary systems are hosted by stars of a wide range of ages, and stellar luminosities evolve with time.
    Since the emergence of a runaway greenhouse phase on a planet is highly dependent on the level of radiation it receives, and thus on the luminosity of the host star, we assigned age-dependent luminosities to our synthetic stars.
    Stellar ages are notoriously poor-constrained (CITE); we thus drew random ages from a uniform distribution from \SI{0}{\giga\year} to \SI{10}{\giga\year}.
    We then assigned each star a luminosity from the mass-dependent evolutionary models in \citet{Baraffe1998}.
    Figure~\ref{fig:luminosity_tracks} shows the corresponding luminosity evolution as a function of stellar mass and age.

@@

>>>>

\subsubsection{Stellar sample from Gaia DR3}
\todo[inline]{KEVIN: describe stellar population}

\subsubsection{Stellar luminosity tracks}
\begin{note}
    Planetary systems are hosted by stars of a wide range of ages, and stellar luminosities evolve with time.
    Since the emergence of a runaway greenhouse phase on a planet is highly dependent on the level of radiation it receives, and thus on the luminosity of the host star, we assigned age-dependent luminosities to our synthetic stars.
    Stellar ages are notoriously poor-constrained (CITE); we thus drew random ages from a uniform distribution from \SI{0}{\giga\year} to \SI{10}{\giga\year}.
    We then assigned each star a luminosity from the mass-dependent evolutionary models in \citet{Baraffe1998}.
    Figure~\ref{fig:luminosity_tracks} shows the corresponding luminosity evolution as a function of stellar mass and age.

@@

\subsubsection{Orbital and bulk properties of the planet sample}

\todo[inline]{GALEN: Describe underlying planet occurrence rates of synthetic population, its Mstar dependency, any caveats or assumptions. Probably replace SAG13-based content below.}
\begin{note}
    The NASA Exoplanet Program Analysis Group chartered Science Analysis Group 13 (SAG 13)...
    The inferred occurrence rate density can be expressed as a power law in planet radius and period
    \begin{equation}
        \frac{\partial^2n}{\partial \log R \, \partial \log P} = \Gamma R^{\alpha} P^{\beta}
    \end{equation}
that is broken in planet radius, resulting in the free parameters $\Gamma$, $\alpha$, $\beta$, and a breakpoint radius $R_\mathrm{break}$.
\end{note}

\begin{note}
    ...
    In this study, we consider only rocky planets with a maximum mass of \SI{2}{\Mearth}. % (Turbet+2020 goes only up to 2 Mearth)

    ...
    To assign masses to our planets, we use the theoretical mass-radius relationship derived in \citet{Zeng2016}.
    The default relation our planets follow is one assuming a pure $\mathrm{MgSiO_3}$ composition. 
    \todo[inline]{JUSTIFY this choice}
    This represents the baseline bulk density before any magma ocean-related effects are applied.
\end{note}
